Refinements for open automata

### 2022-02-03 2021-Refinement/paper/refinementarticle.tex
work on proof and minor things

- reflexivity and transitivity

We will  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.

\begin{lemma} The relation \(\wrel{}{}{H}\) is a preorder thus enables stepwise refinement.
\end{lemma}
The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that \TODO{finish the sentence}\\

@@

@@

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove the following:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$ and $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$.\\
By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
Composing with a tautology ${\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$  and considering that  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}}  \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

>>>>

The first crucial property of  refinement  is that it is reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata. This property enables stepwise refinement.

The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that the relation is indeed reflexive.

@@

We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$

@@

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove the following:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

\TODO{the subtelty here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
